\papertitle

### 2017-03-23 article-icmc2017.tex
save

\usepackage{icmc2017template}
\usepackage{amssymb}
\usepackage{times}
\usepackage{ifpdf}
\usepackage{soul}
\usepackage{microtype}
\usepackage{polyglossia}
%\usepackage{geometry}
\usepackage{tikz}
\usepackage{listings}

\def\papertitle{Paper Template for ICMC 2017}
\def\firstauthor{First Author}
\def\secondauthor{Second Author}
\def\thirdauthor{Third Author}

@@

\title{Temporal dataflows and their application to generative music}

@@

    \section{Introduction}
    This work explores the association of temporal semantics to standard data flow graphs used in music and signal processing.

@@

    An example would be an audio filter: $p_1$ is a low-pass and $p_2$ a reverb.

@@

    The main problem that arises is that composers may specify relationships between processes, but such processes may not always be active. 
    We start by making the case for an environment associated with the dataflow graph that contains the values of the inputs and outputs.
    Then, since a graph may not always be fully active, we show that it is also meaningful to have implicit connections between nodes of the graph, that will use the environment.
    This allows dynamic routing of the processes according to their temporal order during execution, and extends routing to pattern-matched elements of the environment instead of single values.
    We enumerate four different behaviours regarding the input and output parameters when the nodes are implicitely connected at runtime using the environment: strict, glutton, parallelized, and replaced. 
    Additionnaly, when the node are explicitely connected, we introduce a delay mechanism that allows a computation to happen on data previously produced by another node of the graph.

@@

    \subsection{Examples}

    \subsection{Temporal formalism}

    \begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{images/iscore-example.eps}
        \caption{Part of an i-score scenario, showcasing the temporal syntax used. 
            A full horizontal line means that the time must not be interrupted, 
            while a dashed horizontal line means that the time of this time constraint can be interrupted to proceed 
            to the following parts of the score according to an external event.}
        \label{fig.iscore-example}
    \end{figure}

@@

    That is, if a glutton execution happens in the order of the fig.~\ref{fig.simple}, we get the following execution:

    \begin{itemize}
        \item $t_0$: $f_1$.
        \item $t_1$: $f_2 \circ f_1$.
        \item $t_2$: $f_2$. 
    \end{itemize}

    Instead, if we are in the case of fig.~\ref{fig.simple-reversed}, we get:

    \begin{itemize}
        \item $t_0$: $f_2$.
        \item $t_1$: $f_1 \circ f_2$.
        \item $t_2$: $f_1$. 
    \end{itemize}

>>>>

\usepackage{icmc2017template}
\usepackage{amssymb}
\usepackage{times}
\usepackage{ifpdf}
\usepackage{soul}
\usepackage{microtype}
\usepackage{polyglossia}

\usepackage{tikz}
\usepackage{listings}
\usepackage{subcaption}
\def\papertitle{Temporal dataflows and their application to generative music}
\def\firstauthor{First Author}
\def\secondauthor{Second Author}
\def\thirdauthor{Third Author}

@@

\title{\papertitle}

@@

    \section{Introduction}
    This work explores the association of macroscopic temporal semantics to standard data flow graphs used in music and signal processing.

@@

    An example would be an audio filter: $p_1$ is a low-pass and $p_2$ a reverb; we want the reverb to activate only after an action of a performer and stop after a few seconds.

@@

    The main problem that arises is that composers may specify relationships between processes, but such processes may not always be active. 
    We start by making the case for an environment associated with the dataflow graph that contains the values of the inputs and outputs.
    Then, since a graph may not always be fully active, we show that it is also meaningful to have implicit connections between nodes of the graph, that will use the environment.
    This allows dynamic routing of the processes according to their temporal order during execution, and extends routing to pattern-matched elements of the environment instead of single values.
    We enumerate different behaviours regarding the input and output parameters when the nodes are implicitely connected at runtime using the environment: strict, glutton, parallelized, and replaced. 
    Additionnaly, when the node are explicitely connected, we introduce a delay mechanism that allows a computation to happen on data previously produced by another node of the graph, instead of reading the current tokens.

@@

%    \subsection{Examples}

    \subsection{Temporal formalism}
    This work implicitely uses the OSSIA formalism to provide primitives relative to the evolution of time: time constraints (horizontal lines), time nodes (vertical lines). 
    The elements of its syntax are presented in fig.~\ref{fig.iscore-example}.

    \begin{figure}[h]
        \centering
        \includegraphics[width=0.45\textwidth]{images/iscore-example.eps}
        \caption{Part of an i-score scenario, showcasing the temporal syntax used. 
            A full horizontal line means that the time must not be interrupted, 
            while a dashed horizontal line means that the time of this time constraint can be interrupted to proceed 
            to the following parts of the score according to an external event.}
        \label{fig.iscore-example}
    \end{figure}

@@

    \begin{figure}
    	\begin{subfigure}{0.15\textwidth }

    		\begin{itemize}
    			\item $t_0$: $f_1$.
    			\item $t_1$: $f_2 \circ f_1$.
    			\item $t_2$: $f_2$. 
    		\end{itemize}
    		\caption{Glutton execution in the order of the fig.~\ref{fig.simple}}
    	\end{subfigure}~
    \begin{subfigure}{0.15\textwidth}

    	\begin{itemize}
    		\item $t_0$: $f_2$.
    		\item $t_1$: $f_1 \circ f_2$.
    		\item $t_2$: $f_1$. 
    	\end{itemize}
    	\caption{
    		Instead, if we are in the case of fig.~\ref{fig.simple-reversed}, we get: }
    \end{subfigure}
    \caption{}
    \end{figure}
